Make any stupid plot you want

### 2021-01-20 draft/sections/math.tex
extended E

As with fibers and monoids, we can decompose the total space into components 
\begin{equation}
    \pi: E_1 \rightarrow K, \ldots, \pi: E_i \rightarrow K, \ldots \pi: E_n \rightarrow K
\end{equation}

@@

The section $\tau$ is the mapping from base space to total space $\tau: K\rightarrow E$ 
\begin{equation}
    \label{eq:section}
    \begin{tikzcd}
        F \arrow[r, hook] & E \arrow[d, "\pi"']           \\
        & K \arrow[u, "\tau"', bend right]
    \end{tikzcd}
\end{equation}
such that %%insrt math equiality here 
%%% change to b\c locally trivial, can represent 
If the fiber bundle is trivial, then :
\begin{equation}
    \label{eq:section_return}
    \tau(k) = (k, (x_{F_{0}}, \ldots, x_{F_{n}}))
\end{equation}
which is also true when the fiber bundle is locally trivial over $U \subset K$.
%%%can decompose bundles into Ei such that \tau: E_{i} \rightarrow K, where F_{i} is the fiber of E_{i}
which we can also decompose such that
\begin{align}
\tau_{0}(k) &= (k, (x_{F_{0}}))\\
            & \vdotswithin{=}\\
\tau_{n}(k) &= (k, (x_{F_{n}}))
\end{align}

>>>>

As with fibers and monoids, we can decompose the total space into components $\pi:E_i\rightarrow K$ where
\begin{equation}
    \pi:E_1\oplus\ldots\oplus E_i \oplus\ldots \oplus E_n \rightarrow K
\end{equation}

@@

The section $\tau$ is the mapping from base space to total space $\tau: K\rightarrow E$ 
\begin{equation}
    \label{eq:section}
    \begin{tikzcd}
        F \arrow[r, hook] & E \arrow[d, "\pi"']           \\
        & K \arrow[u, "\tau"', bend right]
    \end{tikzcd}
\end{equation}
such that there is $\pi(\tau(k)) = k$ map back to $K$.

If the fiber bundle is locally trivial, then
\begin{equation}
    \label{eq:section_return}
    \tau(k) = (k, (g_{F_{0}}(k), \ldots, g_{F_{n}}(k))
\end{equation}
which is also true when the fiber bundle is locally trivial over $U \subset K$.
%%%can decompose bundles into Ei such that \tau: E_{i} \rightarrow K, where F_{i} is the fiber of E_{i}
which we can also decompose such that
\begin{align}
\tau_{0}(k) &= (k, (x_{F_{0}}))\\
            & \vdotswithin{=}\\
\tau_{n}(k) &= (k, (x_{F_{n}}))
\end{align}
